### 2016-10-01 BF_correctness.tex
fixing BF proof

At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
happens iff there are~$r$ calls to the $\HashOracle$ oracle that
increment~$\err$, i.e., queries $y \not\in S$ such that
$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
does not call~$\HashOracle$ on $y \in S$ because the indices
$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will be
\emph{independent} of those corrsponding to any of the $y \in S$.
Thus these queries are wasted.  Now, there are at total of $q_T + q_H$
queries make to~$\HashOracle$, either directly by~$A$ or indirectly
by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to return 1, there
must be~$r$ among these that increment the counter.  We can assume
WLOG that~$A$ halts as soon as~$\err=r$ (which it can easily track),
so there are $\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query
patterns to consider.  As each error event is independent of all
previous choices made by the~$\HashOracle$, we need only consider the
probability of a single error. Using Kirsch and Mitzenmacher's upper
bound on false positive probability of a classical Bloom filter, 
we have  $\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.

This implies that~$\game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
To summarize, 
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
which is the bound claimed in the theorem statement.
\begin{figure}[tp]
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{0}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

>>>>

At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
happens iff there are~$r$ calls to the $\HashOracle$ oracle that
increment~$\err$, i.e., queries $y \not\in S$ such that
$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
does not call~$\HashOracle$ on $y \in S$ because the indices
$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will be
\emph{independent} of those corrsponding to any of the $y \in S$.
Thus these queries are wasted.  Now, there are at total of $q_T + q_H$
queries made to~$\HashOracle$, either directly by~$A$ or indirectly
by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to return 1, there
must be~$r$ among these that increment the counter.  We can assume
WLOG that~$A$ halts as soon as~$\err=r$ (which it can easily track),
so there are $\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query
patterns to consider.  As each error event is independent of all
previous choices made by the~$\HashOracle$, we need only consider the
probability of a single error. Using Kirsch and Mitzenmacher's~\cite{kirsch2006less} upperbound on false positive probability of a classical Bloom filter, 
we have  $\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
To summarize, 
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
which is the bound claimed in the theorem statement.
\begin{figure}[tp]
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{0}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
